### 2014-11-05 minimax.tex
Small changes.

In Fig.~\ref{results:memory_minmax} we compare the memory usage and scalability
of the coordinated MiniMax against the regular MiniMax. The coordinated version
sees a huge reduction of memory usage, needing at most 8MB for 16 threads, while
the regular version needs around 14GB. Note that as the number of threads goes
up, memory usage also goes up. This is an artifact of our parallel memory
allocator that allocates large chunks of memory before hand.
In terms of run time, our experimental results show linear scalability for the coordinated
version and a 20\% run time reduction when using 16 threads.

>>>>

In Fig.~\ref{results:memory_minmax} we compare the memory usage and scalability
of the coordinated MiniMax against the regular MiniMax. The coordinated version
sees a huge reduction of memory usage, needing at most 8MB for 16 threads, while
the regular version needs around 14GB. Note that as the number of threads goes
up, memory usage also goes up. This is an artifact of our parallel memory
allocator that allocates large chunks of memory beforehand.
In terms of run time, our experimental results show a 14-fold speedup for the
coordinated version against a 12-fold for the regular version when using 16
threads. When comparing the two versions directly, there is a 20\% run time
reduction when using 16 threads in the coordinated version.

### 2014-11-05 sssp.tex
More corrections.
Small changes.

Figure~\ref{results:sssp_uspowergrid} shows experimental results for a variant of
the SSSP program that computes the SSSP for many of the nodes of the graph.
There are some situations where unecessary facts are propagated
because although the shortest distance is selected, sub-optimal distances may be
propagated because many SSSP distances are computed at the same time.
However, we see a reduction of over 50\% in the number of
derived facts when using the coordinated version \textbf{C} over the regular
version \textbf{R}. The results also show that the cordinated
version using 16 threads is 1.3 times faster than the regular version using 16
threads. In turn, this makes the coordinated version 20 times faster
than the regular version using 1 thread.

\begin{figure}[h!]
   \begin{center}
      \subfloat[]{ \begin{tabular}[b]{ | c | c | c | }
         \hline                       
         \textbf{\# T} & \textbf{R} & \textbf{C} \\ \hline \hline
         1 & 333K & 206K \\
         2 & 300K & 210K \\
         4 & 316K & 208K \\
         8 & 328K & 211K \\
         16 & 343K & 212K \\
         \hline  
         \end{tabular}
         \normalsize
      }
      \subfloat[]{\includegraphics[width=5cm]{results/shortest-uspowergrid.png}}
   \end{center}
   \caption{Experimental results for the SSSP program using US powergrid network.
   On the left we show the number of facts derived for the regular \textbf{R}
   and coordinated version \textbf{C} using a variable number of threads
   \textbf{\# T}. On the right, we have the scalability of the regular version
   and coordinated version. The speedup values are computed using the execution
   time of the regular version for 1 thread.}
   \label{results:sssp_uspowergrid}
\end{figure}

>>>>

Figure~\ref{results:sssp_uspowergrid} shows experimental results for a variant of
the SSSP program that computes the SSSP for many of the nodes of the graph.
There are some situations where unecessary facts are propagated
because although the shortest distance is selected, sub-optimal distances may be
propagated because many SSSP distances are computed at the same time.
However, we see a reduction of over 50\% in the number of
derived facts when using the coordinated version \textbf{C} over the regular
version \textbf{R}. The results also show that the cordinated
version using 16 threads is 1.3 times faster than the regular version using 16
threads. In turn, this makes the coordinated version 20 times faster
than the regular version using 1 thread. Note that the coordinated program is as
scalable as the regular program.

\begin{figure}[h!]
   \begin{center}
      \subfloat[]{ \begin{tabular}[b]{ | c | c | c | }
         \hline                       
         \textbf{\# T} & \textbf{R} & \textbf{C} \\ \hline \hline
         1 & 333K & 206K \\
         2 & 300K & 210K \\
         4 & 316K & 208K \\
         8 & 328K & 211K \\
         16 & 343K & 212K \\
         \hline  
         \end{tabular}
         \normalsize
      }
      \subfloat[]{\includegraphics[width=4.5cm]{results/shortest-uspowergrid.png}}
   \end{center}
   \caption{Experimental results for the SSSP program using US powergrid network.
   On the left we show the number of facts derived for the regular \textbf{R}
   and coordinated version \textbf{C} using a variable number of threads
   \textbf{\# T}. On the right, we have the scalability of the regular and
   coordinated version. The speedup values are computed using the execution
   time for 1 thread.}
   \label{results:sssp_uspowergrid}
\end{figure}
